Review: The Extent of Adaptive Wild Introgression in Crops

### 2018-07-05 paper.tex
edits to conclusions

As recognized early on by Darwin, crop species represent promising model systems for evolutionary study. 
The application of genomic tools has generated mounting evidence of crop-wild gene flow during and well beyond the initial stages of domestication.
The process of crop range expansion and adaptation through gene flow is closely linked to domestication and offers new questions and opportunities for practical and theoretical investigation.
Domesticated crops are among humanity's first and greatest inventions.
Interwoven in the genetic history of these crops is the story of our ancestors as they transitioned through the Agronomic Revolution.
In a more nuanced and dynamic understanding of crop domestication that includes sustained gene flow with wild relatives, we gain insight into the evolutionary journey that crops and humanity took, and continue to take, together.

>>>>

Recent innovations in both high-density marker data and methods for characterizing genome-wide patterns of introgression have helped reveal the extent and timing of gene flow in a number of species.
Application of these data and techniques has led to mounting evidence of crop-wild gene flow following initial domestication in several crops.
Substantial post-domestication gene flow with wild relatives can affect inferences made regarding domestication and may be an important mechanism through which crops were able to adapt to novel conditions during global expansions.
An accurate understanding of the extent of gene flow is therefore important to both the basic study of crop evolution and to the identification of adaptive alleles for continued crop improvement.

Domesticated crops are among humanity's greatest inventions.
Interwoven in the genetic history of these crops is the story of our ancestors as they transitioned through the Agricultural Revolution.
In a more nuanced and dynamic understanding of crop domestication that includes sustained gene flow with wild relatives, we gain insight into the evolutionary journey that crops and humanity took, and continue to take, together.
